---
title: "Developing Data Products R Markdown Presentation & Plotly"
author: "Moisés Aarón Ruiz García"
date: "19/11/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Code

Through this code we try to plot the closing prices of major European stock indices in the years of 1991 to 1998.

```{r, echo=TRUE, eval=FALSE}
library(plotly)
library(tidyr)
library(dplyr)
data("EuStockMarkets")
stocks <- as.data.frame(EuStockMarkets) %>%
  gather(index, price) %>%
  mutate(time = rep(time(EuStockMarkets), 4))
plot_ly(stocks, x = ~time, y = ~price, color = ~index, mode = "lines")
```

## Plot

```{r, echo=FALSE, eval=TRUE, message=FALSE}
library(plotly)
library(tidyr)
library(dplyr)
data("EuStockMarkets")
stocks <- as.data.frame(EuStockMarkets) %>%
  gather(index, price) %>%
  mutate(time = rep(time(EuStockMarkets), 4))
plot_ly(stocks, x = ~time, y = ~price, color = ~index, mode = "lines")


Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
